Analysis

### 2019-04-25 reports/DRM_exp/analysis_DRM_exp1.Rmd
start of analysis of DRM exp

---
title: "Analysis"
author: "Filip Dechterenko"
date: "25 června 2018"
output: html_document
---

# Analysis categ

## Load data

```{r load data, warning=FALSE, message=FALSE}
set.seed(167)
load(here::here("data","konkle_180621.RData"))

library(tidyverse)
library(lme4)

theme_set(theme_bw())

data_pth <- here::here("data", "results", "categ")

col_types <- cols(
  .default = col_character(),
  prot_id = col_integer(),
  trial_id = col_integer(),
  target_position = col_integer(),
  quintile = col_integer(),
  trials.thisRepN = col_integer(),
  trials.thisTrialN = col_integer(),
  trials.thisN = col_integer(),
  trials.thisIndex = col_integer(),
  mouse.x = col_double(),
  mouse.y = col_double(),
  mouse.leftButton = col_integer(),
  mouse.midButton = col_integer(),
  mouse.rightButton = col_integer(),
  protocol_id = col_integer(),
  subject_id = col_integer(),
  frameRate = col_double()
)

df <- data_pth %>% 
  dir(pattern = "*.csv", full.names = T) %>% 
  purrr::map(read_csv, col_types = col_types) %>% 
  bind_rows()

df <- df %>%
  mutate(target_image = paste0("image",target_position),
         correct = as.numeric(target_image == mouse.clicked_name),
         category_type = if_else(category %in% c("desert", "waves", "coast", "underwater", "iceberg","field","garden","cavern","beach","canyon","mountainwhite","woods"),"natural","manmade"))

@@

@@

```{r desc stat}
df %>% 
  group_by(quintile) %>% 
  summarize(m = mean(correct) %>% round(2), sd = sd(correct) %>% round(2))

df %>% 
  group_by(category_type) %>% 
  summarize(m = mean(correct) %>% round(2), sd = sd(correct) %>% round(2))

>>>>

---
title: "Analysis"
author: "Filip Dechterenko"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

```{r}
set.seed(190425)
library(tidyverse)
theme_set(theme_bw())
library(lme4)
```

# Load data

```{r load data, warning=FALSE, message=FALSE}

df <- readRDS(here::here("data/exp_DRM1/results_190425.rds"))

@@

df_acc <- df %>% filter(!is.na(correct))
```

@@

```{r desc stat}
df_acc %>% 
  group_by(type) %>% 
  summarize(m = mean(correct), sd = sd(correct)) %>% 
  knitr::kable(digits = 2)

df_acc %>% 
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) +
  stat_summary(fun.data = "mean_cl_boot") +
  ylim(0,1) + theme(aspect.ratio = 1)

df_acc %>% 
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) +
  geom_point() +
  ylim(0,1) + theme(aspect.ratio = 1) +
  facet_grid(~subject_id)

df %>% group_by(subject_id) %>% 
  summarize(correct = mean(correct),
            zH = qno)
